A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
Point 1
Related work (Point 2)

\vspace{1ex}
\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more statement types, and we have studied replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair, an orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique, and show that doing so results in higher-quality repairs; 
we study their templates heuristically on
a different dataset. Their results motivate
studies of human repairs, as it may result in better patches.
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new technique.  Rather, it serves as a starting
point for research on the repair of Java bugs.

@@

\section{Statement-level mutations}
\begin{table*}
	\centering
	\resizebox{\textwidth}{!}{
	%\renewcommand{\arraystretch}{0.9}% Tighter
		\begin{tabular}{l|rrrrrrrrrrrrrrr} \toprule
			&\texttt{Assert}&\texttt{Break}&\texttt{Continue}&\texttt{Do}&\texttt{For}&\texttt{If}&\texttt{Label}&\texttt{Return}&\texttt{Case}&\texttt{Switch}& \texttt{Synch}&\texttt{Throw}&\texttt{Try}&\texttt{TypeDecl}&\texttt{While}
			\\ \midrule

@@

An important study that works as a great complement for this study is~\cite{martinez2013}, in which they discuss a probability distribution for when to apply which kind of edit, meanwhile we go finer grain and discuss a probability distribution of each statement type, once the program has already chosen a kind of edit. It is also worth mentioning that this paper has studied 14 repositories with 89,993 versioning transactions, while our study studies 380,125 repositories with 23,229,406 revisions.

@@

>>>>

\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much
larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more
statement types, and we have studied replacements, omitted from Zhong and Su's
analysis. Similar to our study in Section~\ref{sec:stmtstudy}, researchers have
studied AST-level changes~\cite{Martinez:2015ez} or line
changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
Although granularity differs, our approach is novel with respect to scale of
analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
understand the ``Plastic Surgery Hypothesis'' underlying certain types of
program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
analyze changes to Java programs to inform an automated repair technique, and
show that doing so results in higher-quality repairs; we study their templates
heuristically on a different dataset. Their results motivate studies of human
repairs, as it may result in better patches.  Long and Rinard learn
probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
significantly less precise and does not inform a new technique.  Rather, it
serves as a starting point for research on the repair of Java bugs.

@@

\section{Statement-level mutations}\label{sec:stmtstudy}
\begin{table*}
	\centering
	\resizebox{\textwidth}{!}{
	%\renewcommand{\arraystretch}{0.9}% Tighter
		\begin{tabular}{l|rrrrrrrrrrrrrrr} \toprule
			&\texttt{Assert}&\texttt{Break}&\texttt{Continue}&\texttt{Do}&\texttt{For}&\texttt{If}&\texttt{Label}&\texttt{Return}&\texttt{Case}&\texttt{Switch}& \texttt{Synch}&\texttt{Throw}&\texttt{Try}&\texttt{TypeDecl}&\texttt{While}
			\\ \midrule

@@

@@

An important study that complements for our study is the repair model approach
proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, in which they discuss
a probability distribution for when to apply which kind of edit. Although their
approach is able to trace more fine-grain AST-level changes, our results are
consistent with their findings. For example, their empirical
analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
and variable declaration statements are added/deleted/updated most often, which
is also illustrated in Figure~\ref{fig:StmtType} (In Boa, method invocation and
variable declaration fall into the category of expression). It is also worth
mentioning that their study covers 14 repositories with 89,993 versioning
transactions, while our study studies 380,125 repositories with 23,229,406
revisions.
